Hierarchical storage management in user space for neuroimaging applications

### 2024-03-13 paper/sea-neuro/paper-neuro.tex

The HCP dataset obtained the greatest speedups with
Sea, with $2.3\times$ on average vs $1.3\times$ for PREVENT-AD and $1.9\times$ for ds001545.
Out of the three datasets, HCP has the largest images (see
Table~\ref{table:sea-neuro:data}). Larger individual images mean that they
occupy more page cache space and take longer to flush to Lustre. Unsurprisingly,
the next dataset with the largest images (\SI{282}{\mebi\byte} compressed for a
single image) results in the next largest speedups, followed by PREVENT-AD, the
dataset with the smallest functional images.

@@

Baseline performance without busy writers was comparable to that of Sea's as can be seen in Figure~\ref{fig:seaneuro:slashbin} (p=0.7, two-sample unpaired T-test). However, with
busy writers, the makespan obtained with Sea was smaller than baseline (p<1e-04, two-sample T-test). We did occasionally observe slowdowns from using Sea. These slowdowns
may arise from the initial read of the data, as they appeared to occur less
frequently with the SPM pipeline, or due to increased CPU contention caused by Sea's rapid I/O.

@@

To determine the overhead of Sea, we compared the average performance of Sea with
the performance of pipeline executing entirely within memory
(Figure~\ref{fig:seaneuro:tmpfs}). The results demonstrated that Sea and tmpfs
did not lead to significant differences in average makespan (p=0.9, two-sampled unpaired T-test). Given these results, we conclude that the
overhead of Sea is minimal and that the differences in makespan may be
due to Sea's initial reading of the data from Lustre.

@@

    The dedicated cluster was composed of 8
    compute nodes with \SI{256}{\gibi\byte} memory and \SI{125}{\gibi\byte}
    tmpfs, running Centos 8.1.1911.
    Storage on the dedicated cluster consisted of 4 Lustre ZFS storage nodes with 44
    HDD object storage targets (OSTs) and 1 metadata server (MDS) with a single
    metadata target (MDT). The storage nodes were connected to the compute nodes
    via a 20Gbps ethernet connection. The cluster's hardware was similar to that
    of Compute Canada's Beluga cluster.

    Compute Canada's Beluga cluster was used as the production cluster.
    It consisted of a total of 977 compute nodes, of which we
    used up to 16 general compute nodes at a time with \SI{186}{\gibi\byte} of
    available memory, \SI{480}{\gibi\byte} of local scratch SSD space, 2 Intel
    Gold 6148 Skylake @ 2.4 GHz CPUs and Centos 7 installed. Each compute node
    was connected to the Lustre scratch file system via an Mellanox Infiniband
    EDR (100 Gbps) network interconnect. The Lustre scratch file system consists
    of a total \SI{2.6}{\pebi\byte} of space, with 38 OSTs of
    \SI{69.8}{\tebi\byte} each and two MDTs of \SI{3.3}{\tebi\byte}.

>>>>

The HCP dataset obtained the greatest speedups with
Sea, with $2.3\times$ on average vs. $1.9\times$ for ds001545  and $1.3\times$ for PREVENT-AD.
Out of the three datasets, HCP has the largest images (see
Table~\ref{table:sea-neuro:data}). Larger individual images mean that they
occupy more page cache space and take longer to flush to Lustre. Unsurprisingly,
the next dataset with the largest images (\SI{282}{\mebi\byte} compressed for a
single image) results in the next largest speedups, followed by PREVENT-AD, the
dataset with the smallest functional images.

@@

Baseline performance without busy writers was comparable to that of Sea's (p=0.7, two-sample unpaired t-test) as can be seen in Figure~\ref{fig:seaneuro:slashbin}. However, with
busy writers, the makespan obtained with Sea was smaller than baseline (p<1e-04, two-sample t-test). We did occasionally observe slowdowns from using Sea. These slowdowns
may arise from the initial read of the data, as they appeared to occur less
frequently with the SPM pipeline, or due to increased CPU contention caused by Sea's rapid I/O.

@@

To determine the overhead of Sea, we compared the average performance of Sea with
the performance of pipeline executing entirely within memory
(Figure~\ref{fig:seaneuro:tmpfs}). The results demonstrated that Sea and tmpfs
did not lead to significant differences in average makespan (p=0.9, two-sampled unpaired t-test). Given these results, we conclude that the
overhead of Sea is minimal and that the differences in makespan may be
due to Sea's initial reading of the data from Lustre.

@@

    The dedicated cluster was composed of 8
    compute nodes with \SI{256}{\gibi\byte} memory and \SI{125}{\gibi\byte}
    tmpfs, running Centos 8.1.1911.
    Storage on the dedicated cluster consisted of 4 Lustre ZFS storage nodes with 44
    HDD object storage targets (OSTs) and 1 metadata server (MDS) with a single
    metadata target (MDT). The storage nodes were connected to the compute nodes
    via a 20Gbps ethernet connection. The cluster's hardware was similar to that
    of the Beluga cluster at the Digital Alliance of Canada.

    The Beluga cluster was used as the production cluster.
    It consisted of a total of 977 compute nodes, of which we
    used up to 16 general compute nodes at a time with \SI{186}{\gibi\byte} of
    available memory, \SI{480}{\gibi\byte} of local scratch SSD space, 2 Intel
    Gold 6148 Skylake @ 2.4 GHz CPUs and Centos 7 installed. Each compute node
    was connected to the Lustre scratch file system via an Mellanox Infiniband
    EDR (100 Gbps) network interconnect. The Lustre scratch file system consists
    of a total \SI{2.6}{\pebi\byte} of space, with 38 OSTs of
    \SI{69.8}{\tebi\byte} each and two MDTs of \SI{3.3}{\tebi\byte}.
